Figures to insert in text

### 2018-02-23 Chapters/Chapter02.tex
Minor change SDM conclusion

>>>>

We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is avaiable with sdm-framework and other tools already installed. The simulations run in this thesis are promptly available to be re-executed and explored. We invite the reader to take a look and explore a little bit.
